### 2020-05-26 README.Rmd
renamed package and functions

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![R build status](https://github.com/AIMS/data-platform-r/workflows/R-CMD-check/badge.svg)](https://github.com/AIMS/data-platform-r/actions)
![pkgdown](https://github.com/AIMS/data-platform-r/workflows/pkgdown/badge.svg)
[![license](https://img.shields.io/badge/license-CC BY 3.0 AU-lightgrey.svg)](https://choosealicense.com/)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg)](commits/master)
<!-- badges: end -->

@@

Further information about `dataaimsr` and the **AIMS Data Platform API** can be seen on the [project page](https://aims.github.io/data-platform-r).

>>>>

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![R build status](https://github.com/AIMS/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/AIMS/dataaimsr/actions)
![pkgdown](https://github.com/AIMS/dataaimsr/workflows/pkgdown/badge.svg)
[![license](https://img.shields.io/badge/license-CC BY 3.0 AU-lightgrey.svg)](https://choosealicense.com/)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg)](commits/master)
<!-- badges: end -->

@@

Further information about `dataaimsr` and the **AIMS Data Platform API** can be seen on the [project page](https://aims.github.io/dataaimsr).
